Compositional Certified Resource Bounds\ifshort{\vspace{-.15cm}}{}

### 2014-10-29 paper/main.tex
improvements

Available techniques split in two categories.  In the
first one, tools derive impressive bounds for
imperative programs, but are not fully compositional.
Notable recent work like
SPEED~\cite{GulwaniMC09}, KoAT~\cite{BrockschmidtEFFG14},
PUBS~\cite{AlbertAGPZ12}, Rank~\cite{AliasDFG10},
and LOOPUS~\cite{SinnZV14} falls in this category.
They lack compositionality in at least three ways.
First, they all base their analysis on some form of
\emph{ranking-function}.
Since this
is often a local analysis, the loop bounds are expressed
as arithmetic expressions in terms of variables as they
are just before the loop.  This makes it hard to give a
resource bound on sequenced loops or function calls in
terms of the input parameters of a procedure.
XXX MENTION GULWANI PAPER [1] XXX
Second, while all imperative programming languages
provide a function or procedure abstraction, all
available tools are not able to abstract their resource
behavior and have to inline the procedure body to perform
any kind of analysis.  Third, when such a tool fails on
given program, the only way out to get a resource bound
is to rewrite the program.  There is no possibility
of sound interaction with the tool, and manual proofs
cannot be composed with automatically inferred bounds.
One of the biggest challenge in the way of interaction
with these automated tools is that they work on a highly
abstract version of the program that has a lot more
behaviors than the original program.

>>>>

Available techniques split in two categories.  In the
first one, tools derive impressive bounds for
imperative programs, but are not fully compositional.
Notable recent work like
SPEED~\cite{GulwaniMC09}, KoAT~\cite{BrockschmidtEFFG14},
PUBS~\cite{AlbertAGPZ12}, Rank~\cite{AliasDFG10},
and LOOPUS~\cite{SinnZV14} falls in this category.
They lack compositionality in at least three ways.
First, they all base their analysis on some form of
\emph{ranking-function}.
Since this
is often a local analysis, the loop bounds are expressed
as arithmetic expressions in terms of variables as they
are just before the loop.  This makes it hard to give a
resource bound on sequenced loops or function calls in
terms of the input parameters of a procedure.
XXX MENTION GULWANI PAPER [1] XXX
Second, while all imperative programming languages
provide a function or procedure abstraction, available
tools are not able to abstract their resource behavior
and have to inline the procedure body to perform
their analysis.  Third, when such a tool fails on
program, the only way out to get a resource bound is to
rewrite the program.  There is no opportunity for sound
interaction with the tool, for example, manual proofs
cannot be composed with automatically inferred bounds.
One of the toughest challenges in the way of interaction
is that available tools work on a highly abstract version
of the source program. This abstracted program has a lot
more behaviors than the original one and is usually not
able to express memory related operations.
